Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-07-02 paper/main.tex
add caption of group results figure

\todo[inline]{Why done this way? Why is no. 1 the one?}
% intro
For the AO stimulus, we created eight $t$-contrasts that aimed to isolate the PPA and five contrasts for negative control purposes (see Table \ref{tab:ao-contrasts}).
% PPA contrasts
\todo[inline]{settin-related regressors have small event count compared to
geo/groom; probably more importan in discussion}
Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
\texttt{se\_old} were very vague in describing a scene compared to the richness
of a picture. Hence, we assumed smaller probability of successfully isolating
the PPA.
Discussion der Kontraste/Ergebnisse).
% furniture: blurred border between groom and object
Furniture was not included in one of the contrast because it can be considered
as an object or geometry-defining structure of a room.

@@

\todo[inline]{Why done this way? Why is no. 1 the one?}
% intro
For the AV stimulus, we created five contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of cuts.
and five contrasts for negative control purposes.
% no control for frames content
Notably, this was done without an annotation of the visual content depicted in
the frame after each cut and statistically controlling confounding variables.
% cinematographic rationale
The cinematographic rationale was that movie tend to establishing the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie. Later in the movie, the field
sizes of movie shots tend to decrease when switching back to already established
settings (\texttt{vse\_old}). Shots within a recurring settings tend to shift to
depicting persons and objects (\texttt{vpe\_old}) more relevant to the evolved
narrative \citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that simply that activity in the PPA is
greater when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% im Ergebnis
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.

@@

\paragraph{second level (+ alignment)}
% single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject was performed in functional space preserving the orientation of the EPI
images.
% two ways of co-registration
For subsequent second level results, we co-registered the subjects in two ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T1* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T1* template
that served as standard space.
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template.
% MNI152
This reference images was later co-registered to the MNI 152 template with an
affine transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures,

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{group results}
    \label{fig:group-slices}
\end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{indidvidual PPAs}
    \label{fig:subs-thresh-ppa}
\end{figure*}

>>>>

\todo[inline]{Why done this way? Why is no. 1 the one?}
% intro
For the AO stimulus, we created eight $t$-contrasts that aimed to isolate the
PPA and five $t$-contrasts for negative control purposes (see Table \ref{tab:ao-contrasts}).
% PPA contrasts
\todo[inline]{setting-related regressors have small event count compared to
geo/groom; probably more important in discussion}
Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
\texttt{se\_old} were very vague in describing a scene compared to the richness
of a picture. Hence, we assumed smaller probability of successfully isolating
the PPA.
% furniture: blurred border between groom and object
Furniture was not included in one of the contrast because it can be considered
as an object or geometry-defining structure of a room.

@@

\todo[inline]{Why done this way? Why is no. 1 the one?}
% intro
For the AV stimulus, we created five $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind of cuts.
and five $t$-contrasts for negative control purposes.
% no control for frames content
Notably, this was done without an annotation of the visual content depicted in
the frame after each cut and statistically controlling confounding variables.
% cinematographic rationale
The cinematographic rationale was that movie tend to establishing the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie. Later in the movie, the field
sizes of movie shots tend to decrease when switching back to already established
settings (\texttt{vse\_old}). Shots within a recurring settings tend to shift to
depicting persons and objects (\texttt{vpe\_old}) more relevant to the evolved
narrative \citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that simply that activity in the PPA is
greater when participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal}.
% im Ergebnis
Hence, we created varying contrasts comparing a setting occurring for the first
time and cuts within a locale depicted for the first time to cuts into recurring
settings and cuts within a recurring locale.

@@

\paragraph{second level (+ alignment)}
% single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject was performed in functional space preserving the orientation of the EPI
images.
% two ways of co-registration
For the subsequent second level results, we co-registered the subjects in two ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T1* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T1* template
that served as standard space.
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template.
% MNI152
This reference images was later co-registered to the MNI 152 template with an
affine transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures,

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results.  Significant clusters
        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (grey).
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the $t$-contrast comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (geo, groom > all non-geo).
        Red: audio-visual movie (red).}
    \label{fig:group-slices} \end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{individual PPAs}
    \label{fig:subs-thresh-ppa}
\end{figure*}
